An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-21 paper/4.xpg.tex
fixed small part of explanation

Constructions of $pg$ for the replacement, the product and the source/view rearrangements are very clear when just pairing $put$ and $get$ respectively, then doing basic changes.
%
The values of these $pg$ functions are obtained from the final expression in the corresponding sequences. We only use the return keyword to express explicitly the evaluated value of a function in the situation of $Case$.

>>>>

Constructions of $pg$ for the replacement, the product and the source/view rearrangements are simple. We just pair $put$ and $get$, and change them to $pg$.
%
The values of these $pg$ functions are obtained from the final expression in the corresponding sequences. We only use the return keyword to express explicitly the evaluated value of a function in the situation of $Case$.

### 2020-02-21 paper/main.tex
add acknowledgement about reviewers and KAKENHI
fixed small part of explanation

\author{{Kanae Tsushima\inst{1}} \and \break% \orcidID{0000-0002-3383-3389}
  {Bach Nguyen Trong\inst{1}} \and \break %\orcidID{0000-0002-6342-6020}
  {Robert Gl\"{u}ck\inst{2}} \and \break %\orcidID{0000-0001-6990-3935}
  {Zhenjiang Hu\inst{3}}} %\orcidID{0000-0002-9034-205X}

@@

>>>>

\author{{Kanae Tsushima\inst{1}} \and %\break% \orcidID{0000-0002-3383-3389}
  {Bach Nguyen Trong\inst{1}} \and %\break %\orcidID{0000-0002-6342-6020}
  {Robert Gl\"{u}ck\inst{2}} \and %\break %\orcidID{0000-0001-6990-3935}
  {Zhenjiang Hu\inst{3}}} %\orcidID{0000-0002-9034-205X}

@@

\subsubsection*{Acknowledgement}
We thank the anonymous reviewers for valuable comments and suggestions. This work has been partially supported by JSPS KAKENHI Grant Number JP17H06099.
